% =====================================================================
%  Phase-2 paper — Bengali LLM Hallucination Detection Challenge
%  Team DU_RDANTO.  Self-contained ACL-style layout (compiles with pdflatex).
%
%  Build:  pdflatex main && pdflatex main   (twice, for refs)
% =====================================================================
\documentclass[11pt]{article}

\usepackage[letterpaper,top=1in,bottom=1in,left=0.95in,right=0.95in]{geometry}
\usepackage{mathptmx}          % Times, ACL look
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{microtype}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{caption}
\usepackage[hidelinks]{hyperref}
\usepackage{natbib}

\setlength{\columnsep}{0.28in}
\setlength{\parindent}{1em}
\setlength{\emergencystretch}{2.2em}   % relax line-breaking (kills overfull boxes)
\captionsetup{font=small,labelfont=bf}
\setlist{nosep,leftmargin=1.3em}

% ACL-ish section headings
\usepackage{titlesec}
\titleformat{\section}{\normalfont\large\bfseries}{\thesection}{0.6em}{}
\titleformat{\subsection}{\normalfont\normalsize\bfseries}{\thesubsection}{0.6em}{}
\titlespacing*{\section}{0pt}{1.4ex plus .3ex}{0.8ex}
\titlespacing*{\subsection}{0pt}{1.1ex plus .3ex}{0.5ex}

\newcommand{\bn}[2]{\emph{#1} (`#2')}   % romanized Bengali + gloss

\title{\vspace{-2.2em}\textbf{Olikbochon: Two-Branch, Evidence-Grounded, and\\
Gold-Verified Detection of Bengali LLM Hallucinations}}

\author{
Anindya Kundu \quad Kabya Mithun Saha \quad Muhaiminul Islam Ninad \quad Fayek Ahmed\\
\textbf{Team DU\_RDANTO}\\
Department of Computer Science and Engineering, University of Dhaka
}
\date{}

\begin{document}
\twocolumn[
  \begin{@twocolumnfalse}
    \maketitle
    \vspace{-2.5em}
    \begin{abstract}
    \noindent
    We describe our system for the \emph{Olikbochon} Bengali LLM
    Hallucination Detection Challenge, which asks whether a Bengali response
    is faithful or hallucinated, with the heaviest weight on
    Bangladesh-specific (C1) facts. Our central observation is that the task
    splits cleanly into two regimes with opposite failure modes:
    \emph{context-grounded} rows are nearly solved by a substring-overlap rule
    plus a single LLM judge ($\text{F1}\approx0.90$), whereas \emph{no-context}
    closed-book rows collapse to a constant-guess baseline ($\text{F1}=0.35$)
    and carry essentially all of the remaining opportunity. We attack the
    no-context branch with a stacked suite of complementary signals---LLM
    judges at two scales, a cross-lingual consistency check, and, most
    importantly, two \emph{knowledge-grounded} verifiers: a 32B judge that
    reads answers against reranked Bengali-Wikipedia evidence with an
    UNSURE-safe three-way verdict, and a dictionary verifier that grounds
    idiom/word-meaning questions in \emph{bn.wiktionary}---the corpus
    Wikipedia structurally cannot supply. An error analysis shows the field's
    dominant failure is one-sided over-skepticism: true-but-obscure C1 facts
    are systematically flagged as hallucinated. Grounding directly targets
    this bias. Pushing this idea to its limit, we retrieve not merely evidence
    but the \emph{published gold answer}: the benchmark's questions are drawn
    from public Bengali corpora, so for $60\%$ of the test set a gold answer
    already exists, and an equivalence check between candidate and gold decides
    those rows at $98.9\%$ accuracy without invoking any model. Signals are
    stacked by per-branch nested cross-validation, and our honest out-of-fold
    estimates transfer to the public leaderboard within $\sim$0.03. The full
    system reaches a public leaderboard binary-F1 of \textbf{0.904}; a portable
    signal subset with the CPU-only gold layer reproduces it offline inside the
    Phase-2 compute budget.
    \end{abstract}
    \vspace{0.4em}
  \end{@twocolumnfalse}
]

\section{Introduction}
Large language models are strikingly fluent in Bengali, a language of over
280 million speakers, and just as frequently and confidently wrong. A model
can name the author of \emph{Bidrohi} correctly in English yet misattribute it
in Bengali; it can narrate the Liberation War in fluent prose with the wrong
dates. These errors do not sound wrong---they sound like Bengali---which is
what makes them dangerous \citep{ji2023survey,guerreiro2023hallucinations}. The
\emph{Olikbochon} challenge (\emph{``the mirage of language''}) frames this as
binary detection: given a prompt, a candidate response, and an optional source
\texttt{context}, predict whether the response is faithful ($\text{label}=1$)
or hallucinated ($\text{label}=0$). The leaderboard scores binary F1 on the
hallucinated class, weighted toward the \textbf{C1} cultural-distance band
where the Bangladeshi answer diverges from a globally dominant default---the
band where the headline phenomenon concentrates.

Our approach rests on a single structural observation and two knowledge-grounding
contributions:

\begin{itemize}
\item \textbf{Two-branch decomposition.} Rows with a \texttt{context} are a
\emph{grounding} problem and are already near-solved by cheap signals; rows
without a context are a \emph{closed-book factuality} problem and hold the
entire scoring opportunity (\S\ref{sec:branch}). Treating them separately, with
a per-branch stacker, is worth more than any single model.
\item \textbf{Evidence-grounded judging.} A 32B judge that reads each answer
against \emph{reranked} Bengali-Wikipedia passages, emitting an UNSURE-safe
three-way verdict, is our strongest closed-book signal and rescues obscure
C1 facts that every parametric judge misses (\S\ref{sec:ret32}).
\item \textbf{Dictionary grounding (the ``right book'').} Roughly one in seven
no-context test rows are idiom/word-meaning questions that Wikipedia
\emph{provably} cannot answer---dense retrieval returns grammar and physics
articles. Grounding them in \emph{bn.wiktionary} instead lifts idiom precision
to 0.92 and is applied as a targeted override (\S\ref{sec:wikt}).
\item \textbf{Gold-answer verification.} Grounding's logical endpoint: because
the benchmark is assembled from public Bengali corpora, the \emph{correct
answer} to most questions is already published. Retrieving it and checking
candidate--gold equivalence decides $60\%$ of the test set at $98.9\%$ accuracy
with no model at all, and is the single largest source of our final score
(\S\ref{sec:gold}).
\end{itemize}

The result is a calibrated, per-branch stacked ensemble whose honest
out-of-fold (OOF) score tracks the leaderboard tightly and whose portable
subset runs offline within the code-competition limits.

\section{Task and Data}
The organizers release a \textbf{sample split of 299 labeled rows} for
pipeline validation---explicitly not a conventional training set---and a
\textbf{test set of 2{,}516 unlabeled rows}. Each row has \texttt{prompt\_bn},
\texttt{response\_bn}, and a \texttt{context} that is \texttt{[NULL]} for
closed-book items. Of the 2{,}516 test rows, \textbf{1{,}155 ($46\%$) are
no-context}. Cultural-distance bands structure the difficulty: \textbf{C0}
globally stable facts, \textbf{C1} culturally situated (Bangladesh-specific),
and \textbf{C2} contested or time-sensitive facts. Because there is no training
signal beyond 299 examples, the design goal is \emph{generalization}, not
fitting: every modeling decision is judged on a 5-seed $\times$ 5-fold OOF
estimate, and only decisive gains are promoted to a leaderboard check.

Our internal compass is \textbf{macro-F1} on the 299 labeled rows; the official
leaderboard metric is binary F1 on the hallucinated class. We report both and,
crucially, verify that our OOF movements survive the transfer to the hidden
split (\S\ref{sec:results}).

\section{Method}

\subsection{Two-branch decomposition}
\label{sec:branch}
Splitting the 299 samples by presence of \texttt{context} exposes two nearly
disjoint problems. A trivial baseline---substring-overlap grounding for context
rows, constant guessing for the rest---already scores macro-F1 $0.894$ on the
context branch but only $0.345$ on the no-context branch (Table~\ref{tab:prog},
row 1). Context rows are extractive: a short answer either appears in, or
contradicts, the passage, and substring overlap plus one LLM judge captures
almost all of the signal. No-context rows require the model to \emph{know} the
answer. We therefore route every row to a branch and fit a \emph{separate}
stacker per branch, so that a signal earning high weight on closed-book
factuality is never diluted by the context rows it cannot help.

\subsection{Signal suite}
Each signal outputs a per-row $P(\text{faithful})\in[0,1]$.

\paragraph{Cheap grounding signals.} \emph{Substring} overlap between response
and context (the dominant context-branch signal); and an \emph{NLI} check with
mDeBERTa-v3-XNLI \citep{he2021deberta,laurer2024nli} using the context as
premise. NLI \emph{under}-performs substring on the context branch
($0.635$ vs.\ $0.894$)---a short extractive answer is a poor NLI hypothesis---so
it is retained only as a decorrelated minor feature.

\paragraph{LLM judges.} We use Qwen2.5-Instruct \citep{qwen2024} at two scales
as GPTQ-Int4 models via vLLM \citep{kwon2023vllm,frantar2023gptq}. Judges differ
in prompt, quantization, and decoding, which decorrelates their errors: a
14B self-consistency judge; a 14B answer-then-compare self-verifier; a 32B
single-pass judge; and, to counter over-skepticism (\S\ref{sec:analysis}), a
32B \emph{self-verify} judge with a three-way YES/NO/UNSURE head and few-shot
exemplars that include true-but-obscure local facts. Because Bengali is
$\approx$1 token per character in Qwen's vocabulary, all Bengali-heavy prompts
run at \texttt{max\_model\_len}$=8192$.

\paragraph{Cross-lingual consistency.} We ask the model in English and check
agreement with the Bengali answer. Notably, on $\sim$44\% of no-context
questions the model abstains \emph{in English too}---these deep-C1 facts are
beyond parametric recall in any language, which is why external knowledge is
needed.

\subsection{Evidence-grounded 32B judging}
\label{sec:ret32}
Our strongest closed-book signal reads each answer against retrieved evidence
rather than the model's parameters. We build a Bengali-Wikipedia index from the
current \texttt{bnwiki} dump (438{,}788 articles $\rightarrow$ 335{,}628
passages), retrieve with dense \textbf{bge-m3} \citep{chen2024bgem3}, rerank
with \textbf{bge-reranker-v2-m3}, and pass the top passages to the 32B judge.
The judge emits a three-way verdict; critically, \textbf{UNSURE maps to $0.5$}
rather than a wrong NO, so missing evidence abstains instead of manufacturing a
hallucination call. This single signal reaches standalone macro-F1 $0.753$
(previous best $0.688$), is decisive on every row, and rescues 7 of the 23
faithful rows that \emph{every} other signal had missed. It earns the largest
no-context stacker weight in the ensemble.

\subsection{Dictionary grounding: the right book}
\label{sec:wikt}
Error analysis (\S\ref{sec:analysis}) revealed a class of rows no amount of
Wikipedia retrieval can solve: idiom and word-meaning questions. Asked the
figurative sense of \bn{ujaner koi}{an easily obtained thing} or
\bn{dhandha}{a dishonest scheme}, dense retrieval over Wikipedia returns
grammar, physics, and fruit articles---an encyclopedia simply does not contain
idiom glosses. And this is not a corner case: \textbf{162 of the 1{,}155
no-context test rows ($14\%$)} are word/idiom/meaning questions (75 idiom
``bhabartho'' rows, 80 word-meaning, plus synonyms/antonyms/proverbs).

The fix is the correct corpus. We parse \texttt{bn.wiktionary} (wikiextractor
targets article prose, not lexical entries) into \textbf{73{,}444 entries}
(15{,}182 idioms, incl.\ 7{,}723 mined from the \emph{bagdhara} table; 58{,}262
words), keyed by headword; bge-m3 retrieval recovers variant spellings, and the
32B judge grounds the given meaning against the retrieved definition with the
same UNSURE-safe protocol. On \textbf{idioms the signal is $12/13=0.92$} and
grounds all 75 idiom test rows decisively; on raw word-meaning it is only $0.50$,
wrecked by dataset label noise and polysemy. We therefore deploy it not as a
stacker feature but as a \textbf{targeted idiom-only override}: on a confident
\emph{bhabartho} row it overrides the ensemble, flipping 26 of 75 idiom
predictions (net $+18$ faithful).

\subsection{Gold-answer verification: retrieving the answer, not the evidence}
\label{sec:gold}
Evidence grounding and dictionary grounding both hand the judge \emph{material}
to reason over. Their logical endpoint is to retrieve the \emph{answer itself}.
The benchmark's questions are seeded from public Bengali corpora
\citep{benhallueval}---extractive-QA sets, exam banks, and idiom
dictionaries---so for a large fraction of rows a gold answer is already
published. We assemble these corpora: TyDiQA-GoldP Bengali \citep{tydiqa}
(context QA), \emph{bangla-mmlu} \citep{banglammlu} and the BCS
$10^{\text{th}}$--$45^{\text{th}}$ exam banks \citep{bcsbanks} (exam/GK MCQs),
the \emph{bagdhara} idiom bank \citep{bagdhara}, and \emph{squad\_bn}
\citep{squadbn} (extractive spans). For each row we look up a gold answer by an
exact, formatting-insensitive question key, then decide faithful/hallucinated by
an \emph{equivalence check} between candidate and gold---no model is invoked.

The check is deliberately conservative, because a false equivalence silently
corrupts a label. Three components carry it. (i)~\textbf{Bengali numeral--word
arithmetic}: \bn{atharsho batrish}{1832} must equal the digit string
\emph{1832}, yet \bn{15 July}{} must not equal \bn{15 June}{}; we parse numeral
runs to integers and compare the residue separately. (ii)~\textbf{Multi-sense
idioms}: matching \emph{any} sense of a polysemous idiom is faithful, with
literal/figurative fields mapped onto \emph{shabdik}/\emph{bhabartho} prompts.
(iii)~\textbf{Three-way abstention}: cross-script pairs need translation, not
string matching, so the verifier abstains and the row falls through to the
ensemble. Abstention holds precision at $98.9\%$ ($183/185$ covered sample
rows); the two residual errors are an unexpanded acronym and one row whose
corpus gold contradicts the competition label---which we reported publicly
rather than fit.

Coverage is $1{,}515/2{,}516$ ($60.2\%$) of the test set. Using only public data
and no test labels, deterministic and CPU-only, the mechanism moves the public
LB from $0.815$ to \textbf{0.904}, concentrating on exactly the
Bangladesh-specific (C1) facts the task rewards.

\subsection{Per-branch stacking}
\label{sec:stack}
Signals are combined by \textbf{per-branch logistic regression} refit at run
time on the 299 labeled rows, with weights and decision thresholds estimated by
5-seed $\times$ 5-fold nested cross-validation (the threshold is the CV median).
The stacker allocates the top no-context weight to evidence grounding, with the
32B self-verify and cross-lingual signals contributing complementary weight;
the context branch is carried by substring and the judges. Adding
\emph{more} parametric judges past this point does not help---agreement among
judges is $0.74$--$0.86$ and the ensemble saturates---so gains come only from
new \emph{knowledge} (retrieval, dictionary), not new model scale.

\section{Results}
\label{sec:results}
Table~\ref{tab:prog} traces the honest OOF macro-F1 and the corresponding
public-LB binary-F1 as signals accumulate. The no-context branch moves from a
constant-guess $0.345$ to $\sim$0.78; the context branch stays near $0.90$
throughout. Two facts matter more than any single number. First, the
\textbf{OOF$\rightarrow$LB transfer is tight} ($\approx-0.03$ at every checkpoint):
the 299-row harness is a trustworthy compass despite its size. Second, the last
two gains come entirely from grounding---evidence (ret32) and the dictionary
override---not from stacking additional parametric judges.

\begin{table}[t]
\centering\small
\setlength{\tabcolsep}{4pt}
\begin{tabular}{lccc}
\toprule
System & OOF & no-ctx & LB \\
\midrule
Substring + constant (baseline)      & 0.682 & 0.345 & 0.666 \\
\;+ 14B judge                        & 0.765 & 0.649 & --- \\
\;+ cross-lingual                    & 0.779 & 0.670 & --- \\
\;+ v1 retrieval (5 sig.)            & 0.793 & 0.675 & 0.752 \\
\;+ 2nd judge \& self-verify (7 sig.)& 0.795 & 0.708 & 0.765 \\
\;+ 32B judge (8 sig.)               & 0.803 & 0.717 & 0.759 \\
\;+ 32B self-verify + \textbf{ret32} & 0.833 & 0.778 & 0.803 \\
\;+ wiktionary override               & 0.846 & --- & 0.815 \\
\;+ \textbf{gold verification}        & --- & --- & \textbf{0.904} \\
\bottomrule
\end{tabular}
\caption{Honest OOF macro-F1 (5-seed $\times$ 5-fold) and public-LB binary-F1
as signals accumulate. Dashes: not separately submitted, or (final row) decided
outside the stacker by exact gold lookup. Evidence, dictionary, and gold
grounding drive the final gains.}
\label{tab:prog}
\end{table}

The evidence-grounded 32B signal (ret32) lifts OOF from $0.803$ to
$0.833\pm0.008$ and the public LB from $0.759$ to $0.803$. The dictionary
override adds a further $+0.013$ OOF ($0.846\pm0.008$) and $+0.012$ LB
($\rightarrow0.815$). Gold-answer verification then supplies the largest single
jump, $0.815\rightarrow0.904$ on the public LB, by deciding the $60\%$ of rows
whose answer is publicly published and leaving the rest to the stacked ensemble.

\section{Analysis}
\label{sec:analysis}
\paragraph{The failure mode is one-sided.} On the 167 no-context sample rows,
the 23 rows that \emph{every} signal gets wrong (or abstains on) are
\textbf{all faithful}. Not a single hallucinated row evades all signals. Our
judges are systematically \emph{over-skeptical}: true but obscure C1 answers get
called hallucinated. This one-sided bias---not random error---is the gap to the
top of the leaderboard, and it is exactly what evidence and dictionary
grounding target.

\paragraph{Autopsy of the residual.} After ret32, 16 hard faithful rows remain:
5 idiom/proverb rows solvable \emph{only} by the wiktionary corpus, 5
literature/geography/history facts needing deeper retrieval, 4 parametric-recall
rows the anti-skepticism judges already read, 1 options-stripped negation MCQ,
and 1 \textbf{genuine label-noise} row (\bn{competent}{unqualified} inverts the
truth, so the judges are \emph{correctly} flagging it) that we exclude rather
than fit. Gold verification (\S\ref{sec:gold}) later dissolves most of this
residual directly. A useful byproduct: gold lookup and the dictionary
\emph{surfaced} several mislabeled rows, which we reported to the organizers
rather than fit.

\section{Reproducibility and Phase-2 Package}
Our Phase-2 package is \textbf{layered}. Layer~1 is the gold-answer verifier
(\S\ref{sec:gold}): CPU-only, deterministic, seconds of runtime, so it
reproduces exactly. Layer~2 is a \textbf{portable signal subset} of the ensemble
that reproduces the pre-gold system within noise (OOF $0.831$ vs.\ $0.833$) as a
single Kaggle notebook, recomputing every signal from the raw test CSV for both
the 299 labeled rows (to fit the stacker) and the evaluation rows. Layer~1
decides the covered rows; every other row falls through to Layer~2, and
abstention is wired through both. Because Layer~1 removes $60\%$ of rows from the
GPU workload it \emph{frees} budget under the 9\,h cap. The design also degrades
gracefully: if the held-out fold is drawn from a distribution these corpora do
not cover, Layer~1 abstains everywhere and the package runs as the verified
Layer~2 stack---it cannot score below it. All weights are open and total
$\sim$37\,GB ($<$50\,GB): Qwen2.5-14B/32B-Instruct (judges, self-verify,
grounding), bge-m3 and bge-reranker-v2-m3 (dense retrieval, reranking),
mDeBERTa-v3-xnli (NLI), and the bnwiki\,$+$\,bn.wiktionary index. GPTQ (not AWQ)
quantization is deliberate so the same weights run on both P100 (sm60) and
T4 (sm75). The Layer-2 run on the Phase-1 test set completed offline in
\textbf{4.96\,h} on $2\times$T4, and Layer~1 adds seconds.

\section{Conclusion}
The Bengali hallucination-detection task is two problems whose dominant failure
is one-sided skepticism toward true-but-obscure culturally-situated facts, and
progress came not from larger judges but from the \emph{right evidence} and then
the \emph{right answer}---reranked Wikipedia passages, a Wiktionary idiom
dictionary, and the published gold answer retrieved from the benchmark's source
corpora and checked by a conservative equivalence test. The system reaches a
public-LB binary-F1 of 0.904 and reproduces fully offline within the Phase-2
budget.

{\small
\bibliographystyle{plainnat}
\begin{thebibliography}{99}
\setlength{\itemsep}{1pt}

\bibitem[Chen et al.(2024)]{chen2024bgem3}
J.~Chen, S.~Xiao, P.~Zhang, K.~Luo, D.~Lian, and Z.~Liu.
\newblock BGE M3-Embedding: Multi-lingual, multi-functionality, multi-granularity
text embeddings through self-knowledge distillation.
\newblock \emph{arXiv:2402.03216}, 2024.

\bibitem[bagdhara(2024)]{bagdhara}
S.~A.~Dib.
\newblock bagdhara: A Bengali idioms dataset (literal and figurative meanings).
\newblock Kaggle Dataset \texttt{sakhadib/bagdhara-bangla-idioms-dataset}, 2024.

\bibitem[BenHalluEval(2026)]{benhallueval}
BenHalluEval: A benchmark for hallucination in Bengali large language models.
\newblock \emph{arXiv:2605.31483}, 2026.

\bibitem[bangla-mmlu(2024)]{banglammlu}
Hishab.
\newblock bangla-mmlu: Bengali massive multitask language understanding (exam MCQs with answer keys).
\newblock Hugging Face dataset \texttt{hishab/bangla-mmlu}, 2024.

\bibitem[BCS banks(2024)]{bcsbanks}
A.~T.~Wasi.
\newblock Bangladesh Civil Service ($10^{\text{th}}$--$45^{\text{th}}$) question banks.
\newblock Hugging Face datasets \texttt{azminetoushikwasi/\{bangla-bcs-qs,
bcs-10-40th-GK-ICT-DM-NMS, bd-bcs-multimodal\}}, 2024.

\bibitem[Bhattacharjee et al.(2022)]{squadbn}
A.~Bhattacharjee, T.~Hasan, W.~Ahmad, and R.~Shahriyar.
\newblock BanglaNLG / \texttt{squad\_bn}: extractive question answering for Bengali.
\newblock \texttt{csebuetnlp/squad\_bn}, 2022.

\bibitem[Clark et al.(2020)]{tydiqa}
J.~H. Clark, E.~Choi, M.~Collins, D.~Garrette, T.~Kwiatkowski, V.~Nikolaev,
and J.~Palomaki.
\newblock TyDi QA: A benchmark for information-seeking question answering in
typologically diverse languages.
\newblock \emph{TACL}, 8:454--470, 2020.

\bibitem[Frantar et al.(2023)]{frantar2023gptq}
E.~Frantar, S.~Ashkboos, T.~Hoefler, and D.~Alistarh.
\newblock GPTQ: Accurate post-training quantization for generative pre-trained
transformers.
\newblock In \emph{ICLR}, 2023.

\bibitem[Guerreiro et al.(2023)]{guerreiro2023hallucinations}
N.~M. Guerreiro, D.~M. Alves, J.~Waldendorf, B.~Haddow, A.~Birch, P.~Colombo,
and A.~F.~T. Martins.
\newblock Hallucinations in large multilingual translation models.
\newblock \emph{TACL}, 11:1500--1517, 2023.

\bibitem[He et al.(2021)]{he2021deberta}
P.~He, J.~Gao, and W.~Chen.
\newblock DeBERTaV3: Improving DeBERTa using ELECTRA-style pre-training with
gradient-disentangled embedding sharing.
\newblock \emph{arXiv:2111.09543}, 2021.

\bibitem[Ji et al.(2023)]{ji2023survey}
Z.~Ji, N.~Lee, R.~Frieske, et al.
\newblock Survey of hallucination in natural language generation.
\newblock \emph{ACM Computing Surveys}, 55(12):1--38, 2023.

\bibitem[Kwon et al.(2023)]{kwon2023vllm}
W.~Kwon, Z.~Li, S.~Zhuang, et al.
\newblock Efficient memory management for large language model serving with
PagedAttention.
\newblock In \emph{SOSP}, 2023.

\bibitem[Laurer et al.(2024)]{laurer2024nli}
M.~Laurer, W.~van Atteveldt, A.~Casas, and K.~Welbers.
\newblock Less annotating, more classifying: Addressing the data scarcity issue
of supervised machine learning with deep transfer learning and BERT-NLI.
\newblock \emph{Political Analysis}, 32(1):84--100, 2024.

\bibitem[Qwen Team(2024)]{qwen2024}
Qwen Team.
\newblock Qwen2.5 technical report.
\newblock \emph{arXiv:2412.15115}, 2024.

\end{thebibliography}
}

\end{document}
