% Phase-2 paper report — compile with xelatex (Bengali examples need fontspec).
%   latexmk -xelatex paper.tex
\documentclass[11pt]{article}
\usepackage[final]{acl}
\usepackage{times}
\usepackage{latexsym}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{fontspec}
\newfontfamily\bengalifont{Noto Sans Bengali}
\newcommand{\bn}[1]{{\bengalifont #1}}

\title{Believing True Things: Evidence-Grounded Verification for\\Bengali LLM Hallucination Detection}

\author{Anindya Kundu \and Kabya Mithun Saha \and Muhaiminul Islam Ninad \and Fayek Ahmed \\
  Team \textit{DU\_RDANTO} \\
  Department of Computer Science and Engineering, University of Dhaka \\
  \texttt{anindyakundu00@gmail.com}}

\begin{document}
\maketitle

\begin{abstract}
We describe our system for the \bn{অলীকবচন} Bengali LLM Hallucination
Detection Challenge: given a Bengali prompt, a candidate response, and an
optional supporting passage, predict whether the response is faithful or
hallucinated. Our system stacks seven per-row signals---lexical grounding,
multilingual NLI, two open-weight LLM judges (14B and 32B), self-verification,
and retrieval-grounded verification against a Bengali-Wikipedia index---with a
per-branch logistic regression trained on the 299 released samples. Our
central finding is that the errors of judge-based detectors are
\emph{one-sided}: on the no-context split of the validation samples, every row
that all baseline signals got wrong was \emph{faithful}. LLM judges do not
fail by believing hallucinations; they fail by disbelieving true but obscure,
culturally specific facts. Two design responses follow: verdicts with an
explicit \textsc{unsure} lane that maps to neutrality rather than a wrong
``hallucinated,'' and retrieval-grounded verification that can prove obscure
true answers true. These raised our no-context macro-F1 from 0.694 to 0.778
(out-of-fold) and our public leaderboard score from 0.765 to 0.803. We also
report a validation methodology for 299-sample regimes---seed-averaged nested
cross-validation---without which we repeatedly mistook fold noise for
progress, and we release a fully offline, single-notebook reproduction that
recomputes every signal from raw text in under 5 hours on two T4 GPUs.
\end{abstract}

\section{Introduction}

Large language models are increasingly the interface through which Bengali
speakers reach information, and they are fluent enough in Bengali that their
errors read as confident, natural prose. The \bn{অলীকবচন} challenge
operationalizes this problem as binary classification: each row carries a
Bengali prompt, a candidate response, and either a supporting passage
(\emph{context} rows) or \texttt{[NULL]} (\emph{no-context} rows); systems
predict faithful (1) or hallucinated (0). The benchmark spans cultural-distance
bands from globally stable facts (C0) through Bangladesh-specific knowledge
(C1) to contested or time-sensitive facts (C2), and only 299 labeled samples
are released---a validation set, not a training set.

The two row types are different problems. Context rows reduce to
\emph{grounding}: is the response supported by the passage? No-context rows
require \emph{closed-book factuality}: is the response true? Our system
(\S\ref{sec:system}) treats them as separate branches sharing one stacking
recipe. Our contributions are: (i) an error analysis showing that the failure
mode of LLM-judge ensembles on culturally specific content is systematic
over-skepticism toward true facts (\S\ref{sec:analysis}); (ii) an
evidence-grounded verification branch that directly addresses it
(\S\ref{sec:retrieval}); (iii) a validation protocol that survives a
299-sample regime (\S\ref{sec:validation}); and (iv) a fully offline
reproduction package (\S\ref{sec:repro}).

\section{System}
\label{sec:system}

Every signal is a per-row estimate of $P(\text{faithful}) \in [0,1]$, with
$0.5$ meaning ``no information.'' Signals never make decisions; a per-branch
logistic regression stacks them.

\paragraph{Context branch.}
(1)~\textbf{substring}: after stripping punctuation and whitespace, is the
response a substring of the passage? This trivial rule is remarkably strong
(macro-F1 $0.894$ alone) because most context-row responses are short
extractive answers. (2)~\textbf{nli}: max entailment probability of the
response against sentence-packed passage chunks under multilingual mDeBERTa
\cite{laurer2022}. (3--4)~the two LLM judges below, prompted with the passage.

\paragraph{No-context branch.}
(3)~\textbf{judge14} and (4)~\textbf{judge32}: Qwen2.5-14B and
Qwen2.5-32B-Instruct \cite{qwen2.5} (GPTQ Int4 \cite{frantar2023gptq}),
zero-shot YES/NO factuality judgments. (5)~\textbf{selfv14} and
(6)~\textbf{selfv32}: self-verification \cite{manakul2023selfcheckgpt}---the
model answers the question itself, then a second call judges whether its
answer and the candidate agree; the 32B variant uses three-way verdicts with
token-level log-probabilities (below). (7)~\textbf{ret32}: retrieval-grounded
verification (\S\ref{sec:retrieval}).

\paragraph{Soft, three-way verdicts.}
Binary YES/NO parsing discards calibration and, worse, forces a guess when the
model has no basis for one. Wherever a signal feeds the 32B model, we prompt
for \textsc{yes}/\textsc{no}/\textsc{unsure}, read the first generated token's
top-20 log-probabilities, and set
$P(\text{faithful}) = (p_Y + \tfrac{1}{2}p_U)/(p_Y + p_N + p_U)$.
\textsc{unsure} thus lands at $0.5$---neutral for the stacker---instead of
becoming a confidently wrong \textsc{no}.

\paragraph{Stacking.}
Signals are stacked per branch by L2-regularized logistic regression refit on
the 299 samples at inference time. The decision threshold is the median of
per-fold thresholds over $5$~seeds $\times$ $5$~stratified folds, chosen to
maximize macro-F1 on training folds only.

\section{Error analysis: skepticism is the failure mode}
\label{sec:analysis}

With six baseline no-context signals (two judges, two self-verifications,
a cross-lingual check, and a first-version retrieval branch), we examined the
167 no-context validation rows and asked: which rows does \emph{every} signal
get wrong or abstain on? There were 23 such rows, and \textbf{all 23 were
faithful}. Not one hallucinated row evaded every signal. Meanwhile,
inter-judge agreement ranged $0.74$--$0.86$: adding more generic judges adds
correlated skepticism, not information.

The picture is specific: when a response asserts a true but obscure fact---a
Bangladesh-specific date, a dictionary sense of an idiom like
\bn{ধান্ধা}, a grammatical classification---parametric judges of any size
default to disbelief. The gap between our system and a perfect one was not
``detect more hallucinations''; it was ``stop disbelieving true things.''
This reframing drove everything that follows: the \textsc{unsure} lane
(uncertainty must not be spent as a NO vote) and evidence grounding (the only
mechanism that can \emph{prove} an obscure true answer true).

\section{Evidence-grounded verification}
\label{sec:retrieval}

\paragraph{Index.} We chunk Bengali Wikipedia (143{,}069 articles; HF
\texttt{wikimedia/wikipedia}) into 375{,}604 passages of ${\sim}900$
characters, up to six per article, embedded with bge-m3 \cite{bgem3}
(normalized, fp16).

\paragraph{Retrieval.} For each no-context row we embed two queries---the
question alone, and question~$+$~response---take the union of the top-10
neighbors of each, and rerank with bge-reranker-v2-m3 against
``\emph{question} \bn{উত্তর:} \emph{response},'' keeping the top~4.

\paragraph{Grounded judgment.} Qwen2.5-32B receives the evidence passages and
the QA pair and must answer \textsc{yes} (evidence supports the answer),
\textsc{no} (evidence contradicts it or shows a different answer), or
\textsc{unsure} (evidence irrelevant or insufficient), with the instruction to
\emph{never} answer \textsc{no} merely because the evidence does not mention
the answer. This matters: verbatim answer-presence in retrieved evidence is
non-discriminative (38\% of faithful vs.\ 35\% of hallucinated rows), and
roughly 40\% of evidence sets are irrelevant---notably for word-meaning and
grammar questions, where an encyclopedia is the wrong reference. The
\textsc{unsure} lane routes exactly those cases to neutrality.

Standalone, \texttt{ret32} is the strongest no-context signal we measured
(macro-F1 $0.753$ vs.\ $0.688$ for the best judge variant), it recovers 7 of
the 23 unanimously missed faithful rows, and the stacker assigns it the
largest no-context weight ($1.88$).

\section{Validation in a 299-sample regime}
\label{sec:validation}

Two early lessons shaped our protocol. First, we once reported an ensemble at
$0.8059$ out-of-fold; seed-averaging revealed the honest value was
$0.7946 \pm 0.0089$---the gain had been one favorable fold split. Second, a
$+0.009$ OOF ``improvement'' that we submitted \emph{lost} 0.006 on the public
leaderboard. Our protocol therefore: (i) every configuration is scored as the
mean OOF macro-F1 over 5 seeds of 5-fold stratified CV, with thresholds chosen
inside training folds; (ii) differences under ${\sim}0.02$ are treated as
noise; (iii) submissions are spent only on gains that clear that bar. Under
this protocol, local-to-leaderboard transfer was consistently $-0.03$, making
the OOF a reliable compass. We also found that a stacker fit on 167
no-context rows saturates quickly: abstention-indicator features, a
BanglaBERT classifier fine-tuned on the 299 samples (OOF $0.524$, barely
above chance---surface form does not reveal factuality), branch-specific
feature pruning, and regularization sweeps were all neutral to negative.
Signal quality, not stacking sophistication, is the binding constraint.

\section{Results}

\begin{table}[t]
\centering
\small
\begin{tabular}{lccc}
\toprule
System & OOF & no-ctx & LB \\
\midrule
substring + constant & 0.682 & 0.345 & 0.666 \\
+ 14B judge suite & 0.795 & 0.649 & 0.748 \\
5-signal ensemble & 0.793 & 0.675 & 0.752 \\
7-signal (two judges) & 0.795 & 0.694 & 0.765 \\
+ judge32 (binary) & 0.803 & 0.717 & 0.759 \\
\textbf{+ selfv32 + ret32} & \textbf{0.833} & \textbf{0.778} & \textbf{0.803} \\
\midrule
portable 7 (package) & 0.831 & 0.768 & 0.800 \\
\bottomrule
\end{tabular}
\caption{Progression. OOF = 5-seed mean macro-F1 on the 299 samples
(earlier rows re-scored under the final protocol); no-ctx = no-context branch;
LB = public leaderboard. The final row is the fully offline Phase-2 package.}
\label{tab:results}
\end{table}

Table~\ref{tab:results} traces the system. The two interventions motivated by
the error analysis---\textsc{unsure}-safe 32B self-verification and
evidence-grounded verification---account for the largest single jump
($0.803 \rightarrow 0.833$ OOF, $+0.06$ on the no-context branch), and the
public-leaderboard move ($0.765 \rightarrow 0.803$) landed exactly on the
$-0.03$ transfer line. Context-branch performance was near-saturated
throughout ($\sim$0.90; substring and the 32B judge are jointly wrong on only
3 of 132 rows), confirming that closed-book verification of culturally
specific facts is where this task is decided.

\paragraph{Negative results.} Few-shot anti-skepticism prompting produced our
best standalone judge (0.688) and rescued 10/23 hopeless rows, yet
\emph{hurt} when stacked---with 167 training rows the stacker cannot learn
when to trust an aggressive rescuer. Multilingual NLI underperformed the
substring rule on context rows (0.635 vs.\ 0.894): short extractive answers
make poor NLI hypotheses. Fine-tuned BanglaBERT was chance-level, as noted
above.

\section{Reproducibility}
\label{sec:repro}

Our Phase-2 package is a single Kaggle notebook that recomputes all seven
portable signals from raw text---no cached predictions---and refits the
stacker at run time. All artifacts (both Qwen GPTQ checkpoints, three
encoders, a vLLM wheel set for offline installation, and the wiki index) are
pinned as Kaggle artifacts; the notebook runs with internet disabled. Three
signals from Phase 1 (a self-consistency 14B judge, a cross-lingual check,
and the v1 retrieval branch) required a personal workstation; dropping them
costs nothing measurable (OOF $0.831$ vs.\ $0.833$), so the package ships
the portable seven. Verified end to end on the Phase-1 test set: 4.96 hours
on 2$\times$T4 (9-hour budget), 97.7\% prediction agreement with our
submitted system, public LB 0.800 vs.\ 0.803. Engineering notes: Bengali runs
at roughly one token per character in Qwen's vocabulary, so grounding prompts
need an 8{,}192-token window; GPTQ was chosen over AWQ because it runs on
both P100 (sm60) and T4 (sm75).

\section{Limitations and future work}

About a third of the remaining unanimously missed rows are word-meaning and
grammar questions for which Wikipedia is the wrong corpus; a Bengali
Wiktionary index is the obvious next branch. Our wiki snapshot (Nov.\ 2023)
predates recent facts, capping the C2 band. The 299-sample regime caps how
much any stacker can learn; our per-branch linear model with
seed-averaged thresholds is a floor, not a ceiling. Finally, our analysis is
on the released samples; band-level conclusions (C1 vs.\ C2) await the
organizers' post-competition analysis.

\section*{Acknowledgments}
We thank the organizers of Datathon 2.0 and the \bn{অলীকবচন} challenge.

\bibliography{refs}

\end{document}
